---
title: "Homework-5"
author: "Wenting Gao"
output:
  html_document:
    df_print: paged
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{The linear model vignette}
-->

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

##1. Increase the out-of-sample prediction accuracy by extracting predictive features from the images with LASSO and CNN method.

Reference:
http://varianceexplained.org/r/digit-eda/
http://apapiu.github.io/2016-01-02-minst/
https://keras.rstudio.com/articles/examples/mnist_cnn.html
work with patty zhang

#load all the libraries
```{r, eval=FALSE}
rm(list = ls())
library(tidyverse)
library(glmnet)
library(tidyr)
library(ggplot2)
library(readr)
library(tensorflow)
library(moments)
library(keras)
```

```{r, eval=FALSE}
#install_keras()
#Dataset of 60,000 28x28 grayscale images of the 10 digits, along with a test set of 10,000 images.
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y
y_train <- factor(y_train)
y_test <- factor(y_test)

#Reshape the pixel matrix with the above dataset
x_train <- array_reshape(x_train, c(60000, 28^2))
x_test <- array_reshape(x_test, c(10000, 28^2))

#Prepare for CNN method
X_train <- mnist$train$x
X_valid <- mnist$test$x
Y_train <- mnist$train$y
Y_valid <- mnist$test$y
```

```{r, eval=FALSE}
#Train the model without extracted features
set.seed(1129)
s<- sample(seq_along(y_train), 1000)
fit <- cv.glmnet(x_train[s, ], y_train[s], family = "multinomial")

# in-sample prediction accuracy 
preds.train1 <- predict(fit$glmnet.fit, x_train[s, ], s = fit$lambda.min, type = "class")
t1 <- table(as.vector(preds.train1), y_train[s])
sum(diag(t1)) / sum(t1) 

# out-of-sample prediction accuracy
preds.test1 <- predict(fit$glmnet.fit, x_test, s = fit$lambda.min, type = "class")
t2 <- table(as.vector(preds.test1), y_test)
sum(diag(t2)) / sum(t2) 
```

Without intensity and kurtosis, the in-sample prediction accuracy on training dataset is 0.993, and the out-of-sample prediction accuracy on testing dataset is 0.8526.


The following plots compared means of intensity, kurtosis and skeness among different digits in identifying handwrting characters and digits. 

```{r, eval=FALSE}
#From the plot, we can see the intensity means among digits are different, digit 2 has the lowest intensity, while digit 1 has the highest intensity
int_mean<-apply(x_train,1,mean)
label<-aggregate(int_mean,by=list(y_train),FUN = mean)
plot1<-ggplot(data =label,aes(x=Group.1,y=x))+geom_bar(stat = "identity", fill = "#FF6666")
plot1+scale_x_discrete(limits=0:9)+xlab("label")+ylab("intensity value")+ggtitle("Comparison of intensity means")+ theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#From the plot, we can see the value of kurtosis ranged from 4- to 6+
kurtosis<-apply(x_train,1,kurtosis)
klabel<-aggregate(kurtosis,by=list(y_train),FUN = kurtosis)
plot2<-ggplot(data = klabel,aes(x=Group.1,y=x))+geom_bar(stat = "identity", fill = "#FF6666")
plot2+scale_x_discrete(limits=0:9)+xlab("label")+ylab("kurtosis value")+ggtitle("Comparison of kurtosis")+ theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#From the plot, we can see the skewness ranged from 0.3- to 0.6+ 
skewness<-apply(x_train,1,skewness)
slabel<-aggregate(skewness,by=list(y_train),FUN = skewness)
plot3<-ggplot(data = slabel,aes(x=Group.1,y=x))+geom_bar(stat = "identity", fill = "#FF6666")
plot3+scale_x_discrete(limits=0:9)+xlab("digit label")+ylab("skewness")+ggtitle("Comparison of skewness")+ theme(plot.title = element_text(hjust = 0.5))
```

Since their values of the three parameters are very different among different digits and pixels, implying that the above three features may be useful in identifying handwriting characters. The following models would include intensity and kurtosis and check the out-of-sample prediction accuracy.


```{r, eval=FALSE}
set.seed(1129)
#Train the model with intensity
intensity<-as.vector(int_mean)
x_train<-cbind(x_train,intensity)
x_test<-cbind(x_test,as.vector(apply(x_test,1,mean)))
fit <- cv.glmnet(x_train[s,], y_train[s], family = "multinomial")
# in-sample accuracy on training dataset
preds.train2 <- predict(fit$glmnet.fit, x_train[s, ], s = fit$lambda.min, type = "class")
t3 <- table(as.vector(preds.train2), y_train[s])
sum(diag(t3)) / sum(t3) 
# out-of-sample accuracy on testing dataset
preds.test2 <- predict(fit$glmnet.fit, x_test, s = fit$lambda.min, type = "class")
t4 <- table(as.vector(preds.test2), y_test)
sum(diag(t4)) / sum(t4) 
```

With only intensity, the in-sample prediction accuracy on training dataset is 0.994, and the out-of-sample prediction accuracy on test dataset is 0.8541. The out-of-sample prediction accuracy is slightly better than the original model.

```{r, eval=FALSE}
set.seed(1129)
#Add kurtosis only to the model 
kurtosis<-as.vector(kurtosis)
x_train<-cbind(x_train,kurtosis)
x_test<-cbind(x_test,as.vector(apply(x_test,1,kurtosis)))

#With intensity and kurtosis in the features
fit <- cv.glmnet(x_train[s,], y_train[s], family = "multinomial")
preds.train3 <- predict(fit$glmnet.fit, x_train[s, ], s = fit$lambda.min, type = "class")
t5 <- table(as.vector(preds.train3), y_train[s])
sum(diag(t5)) / sum(t5)# prediction accuracy on training dataset, 0.994

# out-of-sample accuracy on testing dataset
preds.test3 <- predict(fit$glmnet.fit, x_test, s = fit$lambda.min, type = "class")
t6 <- table(as.vector(preds.test3), y_test)
sum(diag(t6)) / sum(t6) ## prediction accuracy on testing dataset, 0.8541
```

summarize prediction accuracy
```{r}
training <- c(sum(diag(t1)) / sum(t1), sum(diag(t3)) / sum(t3),sum(diag(t5)) / sum(t5))
testing <- c(sum(diag(t2)) / sum(t2), sum(diag(t4)) / sum(t4),sum(diag(t6)) / sum(t6)) 
prediction <- rbind(training,testing)
colnames(prediction)=c("w/o intensity and kurtosis","intensity only", "intensity and kurtosis")
rownames(prediction) <- c("training","testing")
prediction
```

From table above, the out-of-sample prediction accuracy continues increasing until constant while more features were added to the model. Also the in-sample accuracy on training dataset is always much better than out-of-sample accuracy on testing dataset, so overfitting may occur.

From class, CNN plays an important role in identifying handwrting digits, characters and images. Thus, in order to improve the ou-of-sample prediction accuracy on testing dataset, CNN method is utilized.

```{r, eval=FALSE}
# Define parameters
batch_size <- 128
num_classes <- 10
epochs <- 2 #train 480,000 samples twice

#Input image dimensions
img_rows <- 28
img_cols <- 28

# Split between train and test sets
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y

# Redefine  dimension of train/test inputs
x_train <- array_reshape(x_train, c(nrow(x_train), img_rows, img_cols, 1))
x_test <- array_reshape(x_test, c(nrow(x_test), img_rows, img_cols, 1))
input_shape <- c(img_rows, img_cols, 1)

# Transform RGB values into [0,1] range
x_train <- x_train / 255
x_test <- x_test / 255
cat('x_train_shape:', dim(x_train), '\n')
cat(nrow(x_train), 'train samples\n')
cat(nrow(x_test), 'test samples\n')

# Convert class vectors to binary class matrices
y_train <- to_categorical(y_train, num_classes)
y_test <- to_categorical(y_test, num_classes)

# Define model
model <- keras_model_sequential() %>%
  layer_conv_2d(filters = 32, kernel_size = c(3,3), activation = 'relu',
                input_shape = input_shape) %>% 
  layer_conv_2d(filters = 64, kernel_size = c(3,3), activation = 'relu') %>% 
  layer_max_pooling_2d(pool_size = c(2, 2)) %>% 
  layer_dropout(rate = 0.25) %>% 
  layer_flatten() %>% 
  layer_dense(units = 128, activation = 'relu') %>% 
  layer_dropout(rate = 0.5) %>% 
  layer_dense(units = num_classes, activation = 'softmax')

# Compile model
model %>% compile(
  loss = loss_categorical_crossentropy,
  optimizer = optimizer_adadelta(),
  metrics = c('accuracy')
)
# Train model
model %>% fit(
  x_train, y_train,
  batch_size = batch_size,
  epochs = epochs,
  validation_split = 0.2
)
scores <- model %>% evaluate(
  x_test, y_test, verbose = 0
)
# The final result
cat('Test loss:', scores[[1]], '\n')
cat('Test accuracy:', scores[[2]], '\n')
```

From the output above, the out-of-sample prediction accuracy is 0.98+, greatly larger than 85%, indicating that the out-of-sample prediction has increased via CNN. It shows that CNN plays a better role in identifying handwriting characters than LASSO.

**Note**: CNN result is saved as `problem1_CNN.html` in `Vignette`. 


#2. CASL 8.11.4

First transfer raw data into `Rda` format
```{r,eval=FALSE}
#library(R.matlab)
#emnist <- readMat('/Users/wentinggao/Downloads/emnist-byclass.mat')
#save(emnist, file='emnist.RData')
```

Then split the dataset into training and testing dataset

```{r,eval=FALSE}
library(keras)
library(glmnet)
library(doMC)
load("/Users/wentinggao/Downloads/emnist.Rdata")
# train set
X_train <- emnist$dataset[[1]][[1]]/255
x_train <- array(dim = c(nrow(X_train), 28, 28))
for (i in 1:nrow(X_train)) {
  x_train[i,,] <- matrix(X_train[i,], nrow=28, ncol=28)
}

y_train <- as.vector(emnist$dataset[[1]][[2]])-1
y_train <- to_categorical(y_train, num_classes = 26)
# test set
X_test <- emnist$dataset[[2]][[1]]/255
x_test <- array(dim = c(nrow(X_test), 28, 28))
for (i in 1:nrow(X_test)) {
  x_test[i,,] <- matrix(X_test[i,], nrow=28, ncol=28)
}
y_test <- as.vector(emnist$dataset[[2]][[2]])-1
y_test <- to_categorical(y_test)
x_train <- array_reshape(x_train, c(nrow(x_train), 28, 28, 1))
x_test <- array_reshape(x_test, c(nrow(x_test), 28, 28, 1))

```

```{r,eval=FALSE}
# original model in textbook
model <- keras_model_sequential()
model %>%
  layer_conv_2d(filters = 32, kernel_size = c(2, 2), input_shape = c(28, 28, 1), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_conv_2d(filters = 32, kernel_size = c(2, 2), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_max_pooling_2d(pool_size = c(2, 2)) %>%
  layer_dropout(rate = 0.5) %>%
  layer_conv_2d(filters = 32, kernel_size = c(2, 2), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_conv_2d(filters = 32, kernel_size = c(2, 2), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_max_pooling_2d(pool_size = c(2, 2)) %>%
  layer_dropout(rate = 0.5) %>%
  layer_flatten() %>%
  layer_dense(units = 128) %>%
  layer_activation(activation = "relu") %>%
  layer_dense(units = 128) %>%
  layer_activation(activation = "relu") %>%
  layer_dropout(rate = 0.5) %>%
  layer_dense(units = 26) %>%
  layer_activation(activation = "softmax")
model %>% compile(loss = 'categorical_crossentropy', optimizer = optimizer_rmsprop(), metrics = c('accuracy'))
model %>% fit(x_train, y_train, epochs = 10, validation_data = list(x_test, y_test), batch_size = 128)
# save the model and load the model to save time
# model %>% save_model_hdf5("original_model.h5")
#model <- load_model_hdf5("original_model.h5")
model %>% keras::evaluate(x_test, y_test, verbose = 0)
# modified model
model1 <- keras_model_sequential()
model1 %>%
  layer_conv_2d(filters = 32, kernel_size = c(3, 3), input_shape = c(28, 28, 1), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_conv_2d(filters = 32, kernel_size = c(3, 3), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_max_pooling_2d(pool_size = c(2, 2)) %>%
  layer_dropout(rate = 0.4) %>%
  layer_conv_2d(filters = 32, kernel_size = c(3, 3), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_conv_2d(filters = 32, kernel_size = c(3, 3), padding = "same") %>%
  layer_activation(activation = "relu") %>%
  layer_max_pooling_2d(pool_size = c(2, 2)) %>%
  layer_dropout(rate = 0.4) %>%
  layer_flatten() %>%
  layer_dense(units = 128) %>%
  layer_activation(activation = "relu") %>%
  layer_dense(units = 128) %>%
  layer_activation(activation = "relu") %>%
  layer_dropout(rate = 0.4) %>%
  layer_dense(units = 26) %>%
  layer_activation(activation = "softmax")
model1 %>% compile(loss = 'categorical_crossentropy', optimizer = optimizer_rmsprop(), metrics = c('accuracy'))
model1 %>% fit(x_train, y_train, epochs = 10, validation_data = list(x_test, y_test), batch_size = 128)
# model1 %>% save_model_hdf5("modified_model.h5")
model1 <- load_model_hdf5("modified_model.h5")
model1 %>% keras::evaluate(x_test, y_test, verbose = 0)
```

Two models were built. The first is the model from CASL 8.10.4, and the accuracy on test set is 88.26%. After modifying kernal size (from (2,2) to (3,3)) and dropout rate (from 0.5 to 0.4), the accuracy increased to 90.95%. 


#CASL 8.11.8

Reference: CASL Textbook
```{r}
# casl_nn_init_weights API
# Initiate weight matrics for a dense neural network.
#
# Args:
#     layer_sizes: A vector(numeric) showing the size of each layer
#
# Returns:
#     A list containing initialized weights and biases.
casl_nn_init_weights <- function(layer_sizes){
  len<- length(layer_sizes) - 1
  weights <- vector("list", len)
  
  for (i in seq_len(len)){
    w <- matrix(rnorm(layer_sizes[i] * layer_sizes[i + 1]),
            ncol = layer_sizes[i],
            nrow = layer_sizes[i + 1])
    weights[[i]] <- list(w=w,
                     b=rnorm(layer_sizes[i + 1]))
  }
  weights
}
weight <- casl_nn_init_weights(c(1, 25, 1))
```

```{r}
# casl_util_ReLU API
# Apply a rectified linear unit (ReLU) to a vector / matrix.
#
# Args:
#     vec: A vector(numeric) or matrix(numeric).
#
# Returns:
#     The original input with negative values truncated to 0.
casl_util_ReLU <- function(vec){
  vec[vec < 0] <- 0
  vec 
}
```

```{r}
# casl_util_ReLU_derivative API
# Apply derivative of the rectified linear unit (ReLU).
#
# Args:
#     vec: A vector(numeric) or matrix(numeric).
#
# Returns:
#     Returned with positive values to 1 and negative values to 0.
casl_util_ReLU_derivative <- function(vec){
  res <- vec * 0
  res[vec > 0] <- 1
  res
}
```

```{r}
# casl_util_mad_p API
# Derivative of the mean absolute deviance (MAD).
#
# Args:
#     y: A vector(numeric) of responses.
#     pred: A vector(numeric) of predicted responses.
#
# Returns:
#     Returned current derivative MAD
casl_util_mad_p <- function(y, pred){
  dev <- c()
  for(i in seq_along(pred)){
    if(pred[i] >= y[i]) dev[i] <- 1
    else dev[i] <- -1
  }
  dev
}
```

```{r}
# casl_nn_forward_prop API
# Apply forward propagation to a set of NN weights and biases.
#
# Args:
#     input: A vector(numeric) representing one row of the input.
#     weights: A list of weights built by casl_nn_init_weights.
#     sigma: The activation function.
#
# Returns:
#     A list containing the new weighted responses (z) and
#     activations (a).
casl_nn_forward_prop <- function(input, weights, sigma){
  len <- length(weights)
  z <- vector("list", len)
  a <- vector("list", len)
  
  for (i in seq_len(len)){
    a_i1 <- if(i == 1) input else a[[i - 1]]
    z[[i]] <- weights[[i]]$w %*% a_i1 + weights[[i]]$b
    a[[i]] <- if (i != len) sigma(z[[i]]) else z[[i]]
  }
  list(z = z, a = a)
}
```

```{r}
# casl_nn_backward_prop API
# Apply backward propagation algorithm.
#
# Args:
#     input: A vector(numeric) representing one row of the input.
#     output: A vector(numeric) representing one row of the response.
#     weights: A list created by casl_nn_init_weights.
#     forwardpp_obj: Output of the function casl_nn_forward_prop.
#     sigma_p: Derivative of the activation function.
#     f_p: Derivative of the loss function.
#
# Returns:
#     A list containing the new weighted responses (z) and
#     activations (a).
casl_nn_backward_prop <- function(input, output, weights, forwardpp_obj, sigma_p, f_p){
  z <- forwardpp_obj$z
  a <- forwardpp_obj$a
  len <- length(weights)
  grad_z <- vector("list", len)
  grad_w <- vector("list", len)
  
  for (i in rev(seq_len(len))){
    if (i == len) {
      grad_z[[i]] <- f_p(output, a[[i]])
      }
    else {
      grad_z[[i]] <- (t(weights[[i + 1]]$w) %*% grad_z[[i + 1]]) * sigma_p(z[[i]])
      }
    a_j1 <- if(i == 1) input else a[[i - 1]]
    grad_w[[i]] <- grad_z[[i]] %*% t(a_j1)
    }
  list(grad_z = grad_z, grad_w = grad_w)
}
```

```{r}
# casl_nn_sgd_mad API
# Apply stochastic gradient descent (SGD) to estimate NN.
#
# Args:
#     X: A data(numeric) matrix.
#     y: A vector(numeric) of responses.
#     layers_sizes: A vector(numeric) showing the sizes of layers in NN.
#     epochs: Integer number of epochs to computer.
#     lr: Learning rate.
#     weights: Optional list of starting weights.
#
# Returns:
#     A list containing the trained weights for the network.
casl_nn_sgd_mad <- function(X, y, layer_sizes, epochs, lr, weights=NULL){
  if (is.null(weights)){
    weights <- casl_nn_init_weights(layer_sizes)
  }
  
  # for every individual, update the weights and repeat the procedure over all individuals.
  for (epoch in seq_len(epochs)){
    # propergations
    for (i in seq_len(nrow(X))){ 
      # excute forward propergation
      forwardpp_obj <- casl_nn_forward_prop(X[i,], weights, casl_util_ReLU)
      # excute backward propergation
      backwardpp_obj <- casl_nn_backward_prop(X[i,], y[i,], weights,
                                     forwardpp_obj, casl_util_ReLU_derivative, casl_util_mad_p)
      # update weights matrics
      for (j in seq_along(weights)){
        weights[[j]]$b <- weights[[j]]$b -lr * backwardpp_obj$grad_z[[j]]
        weights[[j]]$w <- weights[[j]]$w -lr * backwardpp_obj$grad_w[[j]]
      }
    }
  }
  weights
}
```


```{r}
# casl_nn_predict function
# Predict values from a training neural network.
#
# Args:
#     weights: List of weights describing the neural network.
#     X_test: A numeric data matrix for the predictions.
#
# Returns:
#     A matrix of predicted values.
casl_nn_predict <- function(weights, X_test){
  p <- length(weights[[length(weights)]]$b)
  y_hat <- matrix(0, ncol = p, nrow = nrow(X_test))
  
  # excute prediction by forward propergation
  for (i in seq_len(nrow(X_test))){
    a <- casl_nn_forward_prop(X_test[i,], weights, casl_util_ReLU)$a
    y_hat[i, ] <- a[[length(a)]]
    }
  y_hat
}
```


```{r}
library(tidyverse)
#Simulate data using MAD
X <- matrix(runif(1000, min = -1, max = 1), ncol = 1)
yn <- X[, 1, drop = FALSE]^2 + rnorm(1000, sd = 0.1)
# change some yn to be very large (outliers)
ind <- sample(seq_along(yn), 100)
yn[sort(ind)] <- c(runif(50, -10, -5), runif(50, 5, 10))
# train and update weights
weights <- casl_nn_sgd_mad(X, yn, layer_sizes = c(1, 25, 1), epochs = 15, lr = 0.01)
# predict with trained weights
y_pred <- casl_nn_predict(weights, X)
# visualiza the true value and predicted value
d <- tibble(x = as.vector(X), y_pred = as.vector(y_pred),
            y = X[, 1]^2, yn = as.vector(yn))
# plot  result with mean absolute deviation
ggplot(d) + 
  geom_point(aes(x = x, y = yn)) +
  geom_point(aes(x = x, y = y_pred, color = "pink", alpha = 1.5)) +
  labs(x = "x", y = "true/predicted", title = "True and Predicted Values with Mean Absolute Deviance (MAD)") +
  theme(legend.position="None") + labs(subtitle="Pink: Predicted; Black: True") +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
```


From the plot, we can see that the predicted value almost overlap with the true points, indicating that with outliers, the predicted values are robust and they are not influenced by outliers. The neural network and stochastic gradient descent algorithm have robustness to outliers when using mean assolute deviance(MAD).

casl_util_mse_derivative API
```{r, echo=FALSE}
# Derivative of the mean squared error (MSE) function.
#
# Args:
#     y: A numeric vector of responses.
#     pred: A numeric vector of predicted responses.
#
# Returns:
#     Returned current derivative the MSE function.
casl_util_mse_derivative <- function(y, pred){
  2 * (pred - y)
}
```

casl_nn_sgd_mse API
```{r, echo=FALSE}
# Apply stochastic gradient descent (SGD) to estimate NN.
#
# Args:
#     X: A numeric data matrix.
#     y: A numeric vector of responses.
#     sizes: A numeric vector giving the sizes of layers in
#            the neural network.
#     epochs: Integer number of epochs to computer.
#     lr: Learning rate.
#     weights: Optional list of starting weights.
#
# Returns:
#     A list containing the trained weights for the network.
casl_nn_sgd_mse <- function(X, y, layer_sizes, epochs, lr, weights=NULL){
  if (is.null(weights)){
    weights <- casl_nn_init_weights(layer_sizes)
  }
  ## for every individual, update the weights; repeat the procedure over all individuals.
  for (epoch in seq_len(epochs)){
    # propergations
    for (i in seq_len(nrow(X))){ 
      # forward propergations
      forwardpp_obj <- casl_nn_forward_prop(X[i,], weights, casl_util_ReLU)
      # backward propergations
      backwardpp_obj <- casl_nn_backward_prop(X[i,], y[i,], weights,
                                     forwardpp_obj, casl_util_ReLU_derivative, casl_util_mse_derivative)
      # update weights
      for (j in seq_along(weights)){
        weights[[j]]$b <- weights[[j]]$b -lr * backwardpp_obj$grad_z[[j]]
        weights[[j]]$w <- weights[[j]]$w -lr * backwardpp_obj$grad_w[[j]]
      }
    }
  }
  weights
}
```


```{r, echo=FALSE}
#Simulate data processing for MSE
X <- matrix(runif(1000, min = -1, max = 1), ncol = 1)
yn <- X[,1,drop = FALSE]^ 2 + rnorm(1000, sd = 0.1)

# change some yn to be very large (outliers)
ind <- sample(seq_along(yn), 100)
yn[sort(ind)] <- c(runif(50, -10, -5), runif(50, 5, 10))

# train and update weights
weights <- casl_nn_sgd_mse(X, yn, layer_sizes = c(1, 25, 1), epochs = 15, lr = 0.01)

# predict with trained weights
y_pred <- casl_nn_predict(weights, X)

# visualiza the true value and predicted value
d <- tibble(x = as.vector(X), y_pred = as.vector(y_pred),
            y = X[,1]^2, yn = as.vector(yn))

# plot results with mean square error
ggplot(d) + 
  geom_point(aes(x = x, y = yn)) +
  geom_point(aes(x = x, y = y_pred, color = "pink", alpha = 1.5)) +
  labs(x = "x", y = "true/predicted", title = "True and Predicted Values with Mean Squared Error (MSE)") +
  theme(legend.position="None") + labs(subtitle="Pink: Predicted; Black: True") +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
```

If we use MSE instead of MAD, the SGD method is not as robust as before. According to the above plot, the predicted values are apart from true values, showing the predicted values are influenced by outliers. 