---
title: "Homework-4"
author: "Wenting Gao"
output:
  html_document:
    df_print: paged
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{The linear model vignette}
-->

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

## CASL Number 2 in Exercises 5.8.
The Hessian matrix in Equation 5.19 is $$H(l) = X^t'diag(p(1-p)X)$$
where they are all inner product;

Since $cond(A)=\frac{\sigma_{max}}{\sigma_min}$, an ill-conditioned Hessian is where condition number is much larger than that of $X'X$. The condition number of a matrix is the ratio of its largest and smallest singular value.\

```{r}
#Generate the specific matrix X:
X <- matrix(c(1, 100, 100, 1), 2, 2)
p <- c(0.5, 0.001)
X
p
```
First, calculate condition number of matrix $X'X$:
```{r}
sgvals<- svd(t(X)%*%X)[["d"]]
cd_1 <- max(sgvals)/min(sgvals)
cd_1
```
Then, calculate the logistic variation of hessian matrix and its condition number:
```{r}
h=t(X)%*%diag(p*(1-p))%*%X
sgvals_h<-svd(h)[["d"]]
cd_2 <- max(sgvals_h)/min(sgvals_h)
```
Compare the two condition numbers:
```{r}
cd_2-cd_1
```
From the value above, we can conclude that, for this specific matrix $X$, the condition number of logistic variation hessian matrix is much larger than that of hessian matrix.


## CASL Number 2 in Exercises 5.8.

```{r}
# Args:
#     X: A numeric data matrix.
#     y: Response vector.
#     family: Instance of an R ‘family‘ object.
#     maxit: Integer maximum number of iterations.
#     tol: Numeric tolerance parameter.
#     lambda: a penalty term
#
# Returns:
#     Regression vector beta of length ncol(X).
irwls_glm<-function(X, y, family, maxit=25, tol=1e-10, lambda){
beta <- rep(0,ncol(X))
for(j in 1:maxit){
  b_old <- beta
  eta <- X %*% beta
  mu <- family$linkinv(eta)
  mu_p <- family$mu.eta(eta)
  z <- eta + (y - mu) / mu_p
  W <- as.numeric(mu_p^2 / family$variance(mu))
  XtX <- crossprod(X, diag(W) %*% X)
  Xtz <- crossprod(X, W * z)
  # Add the penalty 
  V<-XtX+diag(lambda,dim(XtX)[1])
  beta<-solve(V, Xtz)
  if(sqrt(crossprod(beta - b_old)) < tol) break
}
beta
}
``` 

```{r}
# using data to check the result of the function
n <- 1000; p <- 3
beta <- c(0.2, 2, 1)
X <- cbind(1, matrix(rnorm(n * (p- 1)), ncol = p - 1))
mu <- 1 - pcauchy(X %*% beta)
y <- as.numeric(runif(n) > mu)
# Test the function casl_glm_irwls_ridge
beta <- irwls_glm(X, y,
family = binomial(link = "cauchit"),
lambda = 0.1)
beta
```

# Problem 3
Please see sparse_matrix.r in directory R

